Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-11-12 docs/00-manuscripts/mdpi/performance-best-per-learner.tex
ensure that only 122 instead uf 126 bands are used for all feature sets

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run. For 	exttt{regr.featureless} the Task is no applicable and was therefore removed.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & SVM & Relief & 28.12 & 19.12 \\ 
  2 & NRI & Lasso-MBO & No Filter & 31.16 & 15.03 \\ 
  3 & NRI & Ridge-MBO & No Filter & 31.16 & 15.03 \\ 
  4 & - & regr.featureless & No Filter & 31.16 & 15.03 \\ 
  5 & HR & RF & Relief & 31.25 & 14.96 \\ 
  6 & HR & XGBoost & Car & 34.07 & 13.57 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run. For 	exttt{regr.featureless} the Task is no applicable and was therefore removed.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & NRI-VI & SVM & Info Gain & 27.915 & 18.970 \\ 
  2 & NRI & RF & Relief & 30.842 & 12.028 \\ 
  3 & HR & XGBoost & Info Gain & 31.165 & 15.025 \\ 
  4 & NRI & Lasso-MBO & No Filter & 31.165 & 15.025 \\ 
  5 & NRI & Ridge-MBO & No Filter & 31.165 & 15.025 \\ 
  6 & - & regr.featureless & No Filter & 31.165 & 15.025 \\ 
   \hline
\end{tabular}
}
\end{table}

### 2021-11-12 docs/00-manuscripts/mdpi/tune-perc-sel-features.tex
ensure that only 122 instead uf 126 bands are used for all feature sets

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. 'Features (\texttt{\#})' denotes the absolute number of features selected and 'Features (\texttt{\%})' refers to the percentage relative to the overall features available in the training sets for each plot (Laukiz1 = 1249, Laukiz2 = 1357, Luiando = 1507, Oiartzun = 1311). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{llrl}
  \toprule
Learner & Test Plot & Features (\%) & Features (\#) \\ 
  \midrule
\multirow{4}{*}{\specialcell{RF \\ Relief}} & Laukiz1 & 0.21573 & 3/1249 \\ 
   & Laukiz2 & 93.37086 & 1268/1357 \\ 
   & Luiando & 99.97268 & 1507/1507 \\ 
   & Oiartzun & 0.00405 & 1/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{SVM \\ Relief}} & Laukiz1 & 0.06200 & 1/1249 \\ 
   & Laukiz2 & 23.92820 & 325/1357 \\ 
   & Luiando & 20.73514 & 313/1507 \\ 
   & Oiartzun & 4.10636 & 54/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{XGB \\ CMIM}} & Laukiz1 & 98.12213 & 1226/1249 \\ 
   & Laukiz2 & 0.51526 & 7/1357 \\ 
   & Luiando & 30.84900 & 465/1507 \\ 
   & Oiartzun & 83.61298 & 1097/1311 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. 'Features (\texttt{\#})' denotes the absolute number of features selected and 'Features (\texttt{\%})' refers to the percentage relative to the overall features available in the training sets for each plot (Laukiz1 = 1249, Laukiz2 = 1357, Luiando = 1507, Oiartzun = 1311). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{llrl}
  \toprule
Learner & Test Plot & Features (\%) & Features (\#) \\ 
  \midrule
\multirow{4}{*}{\specialcell{RF \\ Relief}} & Laukiz1 & 0.00614 & 1/1249 \\ 
   & Laukiz2 & 16.58887 & 226/1357 \\ 
   & Luiando & 0.06681 & 2/1507 \\ 
   & Oiartzun & 65.06532 & 854/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{SVM \\ Relief}} & Laukiz1 & 0.50917 & 7/1249 \\ 
   & Laukiz2 & 91.95721 & 1248/1357 \\ 
   & Luiando & 0.50917 & 8/1507 \\ 
   & Oiartzun & 19.70660 & 259/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{XGB \\ CMIM}} & Laukiz1 & 93.70844 & 1171/1249 \\ 
   & Laukiz2 & 3.51986 & 48/1357 \\ 
   & Luiando & 0.12474 & 2/1507 \\ 
   & Oiartzun & 85.28181 & 1119/1311 \\ 
   \bottomrule
\end{tabular}
\end{table}
